2016 Brussels Bombings

### 2019-05-26 report/report.Rmd
Add LEBL traffic evolution for comparison
Add European air traffic evolution plot and averages

@@

>>>>

Comparing the traffic evolution to another European airport, like Barcelona (IATA: BCN, ICAO: LEBL)...

```{r, fig.align='center'}
ddr.times(data$real$flights, 'LEBL', event) # for comparison: BCN
```

@@

```{r, fig.align='center'}
dygraph(eu, main = 'European Air Traffic Evolution', ylab = 'Total Number of Flights', width = '100%') %>%
	dyRangeSelector() %>%
	dyLegend(width = '160') %>%
	dyEvent(event[1], 'Airport closes', labelLoc = 'bottom') %>%
	dyEvent(event[2], 'Airport reopens', labelLoc = 'bottom')
```

- Average traffic before: `r format(round(mean(eu[date < event[1], N])))` flights per day
- Average traffic while `r bru` was closed: `r format(round(mean(eu[date >= event[1] & date <= event[2], N])))` flights per day (`r  sprintf('%+.1f', mean(eu[date >= event[1] & date <= event[2], N]) / mean(eu[date < event[1], N]) * 100 - 100)`%)
- Average traffic after `r bru` reopens: `r format(round(mean(eu[date > event[2], N])))` flights per day (`r  sprintf('%+.1f', mean(eu[date > event[2], N]) / mean(eu[date < event[1], N]) * 100 - 100)`%)
